Towards Comparable Active Learning

### 2023-04-20 doc/al_benchmark_paper.tex
resnet dropout cifar10 linear raytune

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparibility}\label{sec:comparibility}
{\color{red} Version: braindump}\\
We split the evaluation model that generates accuracy scores and the model that generates features for the AL agent. \\
This allows for dropout / ensemble approaches to invest more compute to generate features \\
The normal evaluation model is available as a fallback of course \\
This way, the comparison is always fair

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Choosing the Classifier}\label{sec:choosing_the_classifier}
Traditionally, the classifier is chosen per dataset so that it is capable of solving the dataset close to the SOTA performance reported in the literature.
Similar to our hypothesis in section \ref{sec:evaluation} we hypothesize that AL algorithms will perform similarly on small classifiers and more complex ones, so that the overall ranking of algorithms stays the same.
{\color{red} TODO: Transform this into full hypothesis incl. formatting?}\\
On the basis of this hypothesis we opt to use smaller classifiers that still solve the dataset to a reasonable degree.
Smaller classifiers also require fewer labeled datapoints to acquire performance close to the upper bound.
This behavior can be observed in Figure {\color{red} TODO}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparibility}\label{sec:comparibility}
{\color{red} Version: brain dump}\\
We split the evaluation model that generates accuracy scores and the model that generates features for the AL agent. \\
This allows for dropout / ensemble approaches to invest more compute to generate features \\
The normal evaluation model is available as a fallback of course \\
This way, the comparison is always fair

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Choosing the Classifier}\label{sec:choosing_the_classifier}
Traditionally, the classifier is chosen per dataset so that it is capable of solving the dataset close to the SOTA performance reported in the literature.
Similar to our hypothesis in section \ref{sec:evaluation} we hypothesize that AL algorithms will perform similarly on small classifiers and more complex ones, so that the overall ranking of algorithms stays the same.
{\color{red} TODO: Transform this into full hypothesis incl. formatting?}\\
On the basis of this hypothesis we opt to use smaller classifiers that still solve the dataset to a reasonable degree.
Smaller classifiers also require fewer labeled datapoints to acquire performance close to the upper bound.
This behavior can be observed in Figure {\color{red} TODO} \\ [1mm]
For every dataset the chosen architecture's hyperparameters are optimized by to archive maximum upper bound performance.
For an overview of architectures and hyperparameters please refer to Table \ref{tab:architectures}.
\begin{table}
	\centering
	\begin{tabular}{l || l | l l l l}
		Dataset & Architecture & Optimizer & LR & Weight Decay & Dropout \\
		\hline
		Splice & [24, 12] & NAdam & 0.0012 & 5.9e-5 & 0 \\
		DNA & [24, 12] & NAdam & 0.0398 & 3.6e-5 & 0 \\
		USPS & [24, 12] & Adam & 0.0081 & 1.5e-6 & 0 \\
		FashionMnist & linear & - & - & - & - \\
		Cifar10 & linear & - & - & - & - \\
	\end{tabular}
	\caption{Classifier architectures and optimized hyperparameters per dataset. Numbers in brackets signify a MLP with corresponding hidden layers.}
	\label{tab:architectures}
\end{table}
